Computer Science House Constitution

### 2025-02-04 constitution.tex
Fixed additional grammar and phrasing issues for clarity/consistency

% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
\asubsubsection{Selection Process for Incoming RIT Students}
\begin{enumerate}
	\item During spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
	      The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by ResLife.
	\item A subset of applicants will be offered Intro Membership and have the opportunity to participate in the Intro Process defined in \ref{The Evaluation Period}.
	      A subset of Intro Members will be offered On-Floor status and will be able to select a room on floor.
	      The other Intro Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
\end{enumerate}

@@

\asubsubsection{Expectations of Active Members}
Active Members are required to pay dues as stated in \ref{Collection of Dues}, attend all House Meetings and E-Board candidate speeches, and attend at least fifteen of the directorship meetings for each semester in which they are an Active Member.
They are also expected to sign a copy of the Membership Agreement.
\\* \\*
Active Members must participate in at least one major project during the academic year.
Members are required to submit a description for this major project to E-Board for approval.
As an alternative to this requirement, members may instead assist on a large number of CSH activities and projects.
However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
This participation will be evaluated by E-Board.

@@

\asubsection{Alumni Membership Selection}
Active Members who resign from CSH after passing the current operating session's Membership Eval are considered to be Alumni in good standing.
\\*\\*
Active Members who depart house without passing the current operating session's Membership Eval are considered to be Alumni in bad standing.
This may be appealed to E-Board in order to pursue a different outcome, described in \ref{Appeals}.

@@

\asubsection{Honorary and Advisory Membership Privileges}
Honorary and Advisory Members may advise in CSH issues, use CSH facilities, and attend CSH functions.

@@

\asection{Leave of Absence}
A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
CSH recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence.
House will also help reacclimate any returning member back to the culture of House upon their return.
Upon approval of a leave of absence request, the Evals Director is notified and the member's leave is applied immediately.
A member is also allowed to be physically present and also be on a leave of absence.

@@

\begin{enumerate}
	\item A candidate for the OpComm Directorship shall be chosen by the current RTPs.
	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
	\item The candidate is presented to E-Board for approval.
	      This E-Board Meeting is closed to the E-Board Members, RTPs, and members with explicit invitation from E-Board.
	\item All Voting E-Board Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
	      An E-Board Vote is taken to determine whether the candidate is selected for the position.
\end{enumerate}

@@

\asubsubsection{Term}
\begin{enumerate}
	\item The election process for the following year's E-Board members shall begin in the middle of spring semester.
	\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
	\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
	\item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
	\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
	      When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
\end{enumerate}

@@

\asubsection{Selection of a Root Type Person}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Nominations are taken from the RTPs meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
	\item A list of all nominees who have accepted is presented to E-Board for approval.
	      This E-Board Meeting is closed to E-Board Members, RTPs, and members with explicit invitation from E-Board.
	\item If an E-Board Member is a candidate for the office in discussion, the member is absent and their vote is abstained.
	      An E-Board Vote, as described in \ref{Executive Board Vote}, is taken to determine whether the nominations of the RTP(s) are accepted.
\end{enumerate}

>>>>

% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
\asubsubsection{Selection Process for Incoming RIT Students}
\begin{enumerate}
	\item During the spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
	      The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by ResLife.
	\item A subset of applicants will be offered Intro Membership and have the opportunity to participate in the Intro Process defined in \ref{The Evaluation Period}.
	      A subset of Intro Members will be offered On-Floor status and will be able to select a room on floor.
	      The other Intro Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
\end{enumerate}

@@

\asubsubsection{Expectations of Active Members}
Active Members are required to pay dues as stated in \ref{Collection of Dues}, attend all House Meetings and E-Board candidate speeches, and attend at least fifteen of the directorship meetings for each semester in which they are an Active Member.
They are also expected to sign a copy of the Membership Agreement.
\\* \\*
Active Members must participate in at least one major project during the academic year.
Members are required to submit a description for this major project to E-Board for approval.
As an alternative to this requirement, members may instead assist with a large number of CSH activities and projects.
However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
This participation will be evaluated by E-Board.

@@

\asubsection{Alumni Membership Selection}
Active Members who resign from CSH after passing the current operating session's Membership Eval are considered to be Alumni in good standing.
\\*\\*
Active Members who depart house without passing the current operating session's Membership Eval are considered to be Alumni in bad standing.
This may be appealed to E-Board in order to pursue a different outcome, as described in \ref{Appeals}.

@@

\asubsection{Honorary and Advisory Membership Privileges}
Honorary and Advisory Members may advise on CSH issues, use CSH facilities, and attend CSH functions.

@@

\asection{Leave of Absence}
A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or caregiving for a sick family member.
CSH recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence.
House will also help reacclimate any returning member back to the culture of House upon their return.
Upon approval of a leave of absence request, the Evals Director is notified and the member's leave is applied immediately.
A member is also allowed to be physically present and also be on a leave of absence.

@@

\begin{enumerate}
	\item A candidate for the OpComm Directorship shall be chosen by the current RTPs.
	\item The candidate is given a minimum of a twenty-four hour period to accept or decline the nomination.
	\item The candidate is presented to E-Board for approval.
	      This E-Board Meeting is closed to the E-Board Members, RTPs, and members with explicit invitation from E-Board.
	\item All Voting E-Board Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
	      An E-Board Vote is taken to determine whether the candidate is selected for the position.
\end{enumerate}

@@

\asubsubsection{Term}
\begin{enumerate}
	\item The election process for the following year's E-Board members shall begin in the middle of the spring semester.
	\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
	\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
	\item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
	\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
	      When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
\end{enumerate}

@@

\asubsection{Selection of a Root Type Person}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Nominations are taken from the RTPs meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
	\item Each candidate is given a minimum of a twenty-four hour period to accept or decline the nomination.
	\item A list of all nominees who have accepted is presented to E-Board for approval.
	      This E-Board Meeting is closed to E-Board Members, RTPs, and members with explicit invitation from E-Board.
	\item If an E-Board Member is a candidate for the office in discussion, the member is absent and their vote is abstained.
	      An E-Board Vote, as described in \ref{Executive Board Vote}, is taken to determine whether the nominations of the RTP(s) are accepted.
\end{enumerate}
